\documentclass{article}
    \usepackage{pgfplots}
    \usepackage{pgfplotstable}
    \usepackage{tikz}
    \usepackage{xcolor}
    \definecolor{color1}{RGB}{55,126,184}
    \definecolor{color2}{RGB}{228,26,28}
    \definecolor{color3}{RGB}{77,175,74}
    \definecolor{color4}{RGB}{152,78,163}
    \definecolor{color5}{RGB}{255,127,0}
    \usepackage{xifthen}
    \newcommand{\tool}[1]{\textsc{#1}}

    % Quantile plots
    \newlength{\quantileplotwidth}
    \newlength{\quantileplotheight}
    \setlength{\quantileplotwidth}{\linewidth}
    \setlength{\quantileplotheight}{9cm}
    \newcommand{\quantileplotlegendpos}{south east}
    \tikzset{tool/.code={%
            \ifthenelse{\equal{#1}{mcsta}}{\tikzset{red, mark=x, mark options={thick}}}{}%
            \ifthenelse{\equal{#1}{Storm}}{\tikzset{blue,mark=+, mark options={thick}}}{}%
            \ifthenelse{\equal{#1}{Storm-static}}{\tikzset{cyan,mark=+, mark options={thick}}}{}%
            \ifthenelse{\equal{#1}{ePMC}}{\tikzset{green!70!black, mark=*, mark size=1.5pt}}{}%
            \ifthenelse{\equal{#1}{PRISM}}{\tikzset{orange, mark=asterisk}}{}%
            \ifthenelse{\equal{#1}{PET}}{\tikzset{teal, mark=star}}{}%
            \ifthenelse{\equal{#1}{modes}}{\tikzset{magenta, mark=square*,  mark size=1.5pt}}{}%
            \ifthenelse{\equal{#1}{DFTRES}}{\tikzset{yellow,mark=diamond*}}{}%
            \ifthenelse{\equal{#1}{STAMINA}}{\tikzset{gray, mark=pentagon*}}{}%
            \ifthenelse{\equal{#1}{ModestFRETpiLRTDP}}{\tikzset{black, mark=triangle*}}{}%
    }}
    \newcommand{\quantileplot}[2]{%
    \begin{tikzpicture}
        \begin{axis}[
            width=\quantileplotwidth,
            height=\quantileplotheight,
            xmin=1,
            ymax=2300,
    %		ymin=0.5,
            ymin=1,
            ymode=log,
            axis x line=bottom,
            axis y line=left,
            ytick= {1, 6, 60, 600, 1200, 1800 },
            yticklabels={$\le$1, 6, 60, 600, 1200, 1800},
            xlabel=solved instances,
            ylabel=time (in s),
            yticklabel style={font=\scriptsize},
            xticklabel style={rotate=290, anchor=west, font=\scriptsize},
            ylabel style={yshift=-0cm},
            legend pos=\quantileplotlegendpos,
            legend style={font=\scriptsize},
        ]
        \foreach \tool in {#2}{%
            \edef\loopbody{
                \noexpand\addplot[tool=\tool] table [x=n,y=\tool shifted, col sep=semicolon] {#1};
            }
            \loopbody
        }
        \draw[densely dotted] (axis cs: 0,1) -- (axis cs: 100,1);
        \legend{#2}
        \end{axis}
    \end{tikzpicture}%
    }

    %Scatter plots
    \newlength{\scatterplotsize}
    \setlength{\scatterplotsize}{8cm}
    \pgfplotsset{scatteraxisonevsall/.style={%
            ymax=6000,
            xmax=25000,
            extra x ticks = {4000,8000,16000},
            extra x tick labels = {TO,ERR,INC},
            extra y ticks = {4000},
            extra y tick labels = {n/a},
        ylabel style={yshift=-5.1mm,xshift=-2.5mm},
        legend columns=2,
        legend pos=north east,
        legend style={font=\scriptsize,anchor=north west,xshift=11.5mm}
    }}
    \newcommand{\scatterplot}[4]{\pgfplotsset{scatteraxis/.style={scatteraxisonevsall}}\scatterplota{#1}{#2shifted}{#3}{other}{best other}{#4}}
    \newcommand{\scatterplotstorm}[4]{\pgfplotsset{scatteraxis/.style={scatteraxisonevsall}}\scatterplota{#1}{#2shifted}{#3}{other}{\tool{St.}-static}{#4}}
    \pgfplotsset{scatteraxisonevsone/.style={%
            ymax=35000,
            xmax=35000,
            extra x ticks = {4000,7200,12960,23328},
            extra x tick labels = {TO,ERR,INC,n/s},
            extra y ticks = {4000,7200,12960,23328},
            extra y tick labels = {TO,ERR,INC,n/s},
        ylabel style={yshift=-0.25cm},
        legend columns=1,
        legend pos=north east,
        legend style={font=\scriptsize,anchor=north west,xshift=6.5mm}
    }}
    \newcommand{\scatterplottwo}[6]{{\setlength{\scatterplotsize}{0.435\linewidth}\pgfplotsset{scatteraxis/.style={scatteraxisonevsone}}\scatterplota{#1}{#2shifted}{#3}{#4shifted}{#5}{#6}}}
    \newcommand{\scatterplota}[6]{%
    \begin{tikzpicture}
        \begin{axis}[
        scatteraxis,
        width=\scatterplotsize,
        height=\scatterplotsize,
        axis equal image,
        xmin=0.3,
        ymin=0.3,
        xmode=log,
        ymode=log,
        axis x line=bottom,
        axis y line=left,
        xtick={1,6,60,600,1800},
        xticklabels={1,6,60,600,1800},
        extra x tick style = {grid = major},
        ytick={1,6,60,600,1800},
        yticklabels={1,6,60,600,1800},
        extra y tick style = {grid = major},
        xlabel={#3},
        xlabel style={yshift=-2mm,xshift=-2mm},
        ylabel={#5},
        yticklabel style={font=\tiny},
        xticklabel style={rotate=90,anchor=east,font=\tiny},
        legend cell align=left
        ]
        \addplot[
        scatter,
        only marks,
        scatter/classes={
            dtmc={mark=pentagon*,color4,mark size=1.5},
            ctmc={mark=*,color5,mark size=1.33},
            mdp={mark=triangle*,color2,mark size=1.75},
            ma={mark=diamond*,color3,mark size=1.75},
            pta={mark=square*,color1,mark size=1.25}
        },
        scatter src=explicit symbolic
        ]%
        table [col sep=semicolon,x=#2,y=#4,meta=Type] {#1};
        \ifthenelse{\equal{#6}{legend}}{\legend{DTMC~${}$, CTMC, MDP, MA, PTA}}{}
        \ifthenelse{\equal{#6}{legend-1}}{\legend{DTMC, CTMC, MDP, MA, PTA}}{}
        \addplot[no marks] coordinates {(0.01,0.01) (3600,3600) };
        \addplot[no marks, densely dotted] coordinates {(0.01,0.1) (360,3600) };
        \addplot[no marks, densely dotted] coordinates {(0.1,0.01) (3600,360) };
        \end{axis}
    \end{tikzpicture}
    }

    \begin{document}
            \begin{center}
                Quantile plot for 86 benchmarks: mcsta(60/86), Storm-static(68/86), Storm(76/86).Default configuration.
                \quantileplot{tools-mcsta-storm-intersection.csv}{mcsta,Storm-static,Storm}
            \end{center}
                    
            \begin{center}
                Quantile plot for 86 benchmarks: mcsta(61/86), Storm-static(76/86), Storm(76/86).Specific configuration.
                \quantileplot{specifictools-mcsta-storm-intersection.csv}{mcsta,Storm-static,Storm}
            \end{center}
                    \pagebreak

            \begin{center}
                Quantile plot for 56 benchmarks: ePMC(29/56), mcsta(40/56), Storm-static(44/56), Storm(51/56).Default configuration.
                \quantileplot{tools-epmc-mcsta-storm-intersection.csv}{ePMC,mcsta,Storm-static,Storm}
            \end{center}
                    
            \begin{center}
                Quantile plot for 56 benchmarks: ePMC(29/56), mcsta(41/56), Storm-static(51/56), Storm(51/56).Specific configuration.
                \quantileplot{specifictools-epmc-mcsta-storm-intersection.csv}{ePMC,mcsta,Storm-static,Storm}
            \end{center}
                    \pagebreak

            \begin{center}
                Quantile plot for 41 benchmarks: ePMC(26/41), mcsta(30/41), PRISM(38/41), Storm-static(36/41), Storm(41/41).Default configuration.
                \quantileplot{tools-epmc-mcsta-prism-storm-intersection.csv}{ePMC,mcsta,PRISM,Storm-static,Storm}
            \end{center}
                    
            \begin{center}
                Quantile plot for 41 benchmarks: ePMC(26/41), mcsta(31/41), PRISM(39/41), Storm-static(41/41), Storm(41/41).Specific configuration.
                \quantileplot{specifictools-epmc-mcsta-prism-storm-intersection.csv}{ePMC,mcsta,PRISM,Storm-static,Storm}
            \end{center}
                    \pagebreak

            \begin{center}
                Quantile plot for 23 benchmarks: ePMC(15/23), mcsta(18/23), PET(9/23), PRISM(20/23), Storm-static(19/23), Storm(23/23).Default configuration.
                \quantileplot{tools-epmc-mcsta-pet-prism-storm-intersection.csv}{ePMC,mcsta,PET,PRISM,Storm-static,Storm}
            \end{center}
                    
            \begin{center}
                Quantile plot for 23 benchmarks: ePMC(15/23), mcsta(19/23), PET(6/23), PRISM(21/23), Storm-static(23/23), Storm(23/23).Specific configuration.
                \quantileplot{specifictools-epmc-mcsta-pet-prism-storm-intersection.csv}{ePMC,mcsta,PET,PRISM,Storm-static,Storm}
            \end{center}
                    \pagebreak

            \begin{center}
                Quantile plot for 36 benchmarks: ePMC(12/29), mcsta(15/29), modes(19/32), PRISM(24/26), Storm-static(26/36), Storm(33/36).Default configuration.dtmc ctmc
                \quantileplot{tools-mcsta-prism-storm-markov-chains.csv}{ePMC,mcsta,modes,PRISM,Storm-static,Storm}
            \end{center}
                    
            \begin{center}
                Quantile plot for 36 benchmarks: ePMC(12/29), mcsta(16/29), modes(19/32), PRISM(26/26), Storm-static(33/36), Storm(33/36).Specific configuration.dtmc ctmc
                \quantileplot{specifictools-mcsta-prism-storm-markov-chains.csv}{ePMC,mcsta,modes,PRISM,Storm-static,Storm}
            \end{center}
                    \pagebreak

            \begin{center}
                Quantile plot for 100 benchmarks: DFTRES(5/12), ePMC(31/61), mcsta(62/88), modes(19/32), ModestFRETpiLRTDP(11/31), PET(9/24), PRISM(54/58), STAMINA(1/3), Storm-static(77/96), Storm(86/96).Default configuration.
                \quantileplot{all.csv}{DFTRES,ePMC,mcsta,modes,ModestFRETpiLRTDP,PET,PRISM,STAMINA,Storm-static,Storm}
            \end{center}
                    
            \begin{center}
                Quantile plot for 100 benchmarks: DFTRES(6/12), ePMC(31/61), mcsta(63/88), modes(19/32), ModestFRETpiLRTDP(11/31), PET(6/24), PRISM(56/58), STAMINA(1/3), Storm-static(86/96), Storm(86/96).Specific configuration.
                \quantileplot{specificall.csv}{DFTRES,ePMC,mcsta,modes,ModestFRETpiLRTDP,PET,PRISM,STAMINA,Storm-static,Storm}
            \end{center}
                    \pagebreak

            \begin{center}
                Scatter Plot for Storm with default settings (n=96).
                \scatterplot{scatterStorm.csv}{Storm}{\tool{Storm}  (default, fastest on 46/96)}{legend}
            \end{center}
                
            \begin{center}
                Scatter Plot for Storm with specific settings (n=96).
                \scatterplot{scatterspecificStorm.csv}{Storm}{\tool{Storm}  (specific, fastest on 45/96)}{legend}
            \end{center}
                \pagebreak

            \begin{center}
                Scatter Plot for Storm-static with default settings (n=96).
                \scatterplot{scatterStorm-static.csv}{Storm-static}{\tool{Storm-static}  (default, fastest on 28/96)}{legend}
            \end{center}
                
            \begin{center}
                Scatter Plot for Storm-static with specific settings (n=96).
                \scatterplot{scatterspecificStorm-static.csv}{Storm-static}{\tool{Storm-static}  (specific, fastest on 47/96)}{legend}
            \end{center}
                \pagebreak

            \begin{center}
                Scatter Plot for mcsta with default settings (n=88).
                \scatterplot{scattermcsta.csv}{mcsta}{\tool{mcsta}  (default, fastest on 26/88)}{legend}
            \end{center}
                
            \begin{center}
                Scatter Plot for mcsta with specific settings (n=88).
                \scatterplot{scatterspecificmcsta.csv}{mcsta}{\tool{mcsta}  (specific, fastest on 19/88)}{legend}
            \end{center}
                \pagebreak

            \begin{center}
                Scatter Plot for PRISM with default settings (n=58).
                \scatterplot{scatterPRISM.csv}{PRISM}{\tool{PRISM}  (default, fastest on 17/58)}{legend}
            \end{center}
                
            \begin{center}
                Scatter Plot for PRISM with specific settings (n=58).
                \scatterplot{scatterspecificPRISM.csv}{PRISM}{\tool{PRISM}  (specific, fastest on 10/58)}{legend}
            \end{center}
                \pagebreak

            \begin{center}
                Scatter Plot for PET with default settings (n=24).
                \scatterplot{scatterPET.csv}{PET}{\tool{PET}  (default, fastest on 3/24)}{legend}
            \end{center}
                
            \begin{center}
                Scatter Plot for PET with specific settings (n=24).
                \scatterplot{scatterspecificPET.csv}{PET}{\tool{PET}  (specific, fastest on 1/24)}{legend}
            \end{center}
                \pagebreak

            \begin{center}
                Scatter Plot for modes with default settings (n=32).
                \scatterplot{scattermodes.csv}{modes}{\tool{modes}  (default, fastest on 8/32)}{legend}
            \end{center}
                
            \begin{center}
                Scatter Plot for modes with specific settings (n=32).
                \scatterplot{scatterspecificmodes.csv}{modes}{\tool{modes}  (specific, fastest on 6/32)}{legend}
            \end{center}
                \pagebreak

            \begin{center}
                Scatter Plot for DFTRES with default settings (n=12).
                \scatterplot{scatterDFTRES.csv}{DFTRES}{\tool{DFTRES}  (default, fastest on 2/12)}{legend}
            \end{center}
                
            \begin{center}
                Scatter Plot for DFTRES with specific settings (n=12).
                \scatterplot{scatterspecificDFTRES.csv}{DFTRES}{\tool{DFTRES}  (specific, fastest on 2/12)}{legend}
            \end{center}
                \pagebreak

            \begin{center}
                Scatter Plot for STAMINA with default settings (n=3).
                \scatterplot{scatterSTAMINA.csv}{STAMINA}{\tool{STAMINA}  (default, fastest on 0/3)}{legend}
            \end{center}
                
            \begin{center}
                Scatter Plot for STAMINA with specific settings (n=3).
                \scatterplot{scatterspecificSTAMINA.csv}{STAMINA}{\tool{STAMINA}  (specific, fastest on 0/3)}{legend}
            \end{center}
                \pagebreak

            \begin{center}
                Scatter Plot for ModestFRETpiLRTDP with default settings (n=31).
                \scatterplot{scatterModestFRETpiLRTDP.csv}{ModestFRETpiLRTDP}{\tool{ModestFRETpiLRTDP}  (default, fastest on 8/31)}{legend}
            \end{center}
                
            \begin{center}
                Scatter Plot for ModestFRETpiLRTDP with specific settings (n=31).
                \scatterplot{scatterspecificModestFRETpiLRTDP.csv}{ModestFRETpiLRTDP}{\tool{ModestFRETpiLRTDP}  (specific, fastest on 8/31)}{legend}
            \end{center}
                \pagebreak

            \begin{center}
                Scatter Plot for ePMC with default settings (n=61).
                \scatterplot{scatterePMC.csv}{ePMC}{\tool{ePMC}  (default, fastest on 2/61)}{legend}
            \end{center}
                
            \begin{center}
                Scatter Plot for ePMC with specific settings (n=61).
                \scatterplot{scatterspecificePMC.csv}{ePMC}{\tool{ePMC}  (specific, fastest on 3/61)}{legend}
            \end{center}
                \pagebreak

        \begin{center}
            Scatter Plot for Storm vs. Storm-static with default settings (n=96).
            \scatterplotstorm{scatter_storm_vs_static.csv}{Storm}{\tool{Storm}  (default, fastest on 64/96)}{legend}
        \end{center}
            
        \begin{center}
            Scatter Plot for Storm vs. Storm-static with specific settings (n=96).
            \scatterplotstorm{scatter_storm_vs_staticspecific.csv}{Storm}{\tool{Storm}  (specific, fastest on 36/96)}{legend}
        \end{center}
            \pagebreak
\end{document}
